The Next Release Problem in Real World

### 2018-12-18 PaperBody.tex
add heatmap on progress

\begin{figure*}[h]
\centering
  \begin{subfigure}[b]{0.95\linewidth}
    \includegraphics[width=\linewidth]{images/heatmap_ec.png}
  \end{subfigure}
  \caption{EX3-Requirements Heatmap in Eclipse Repositories(white = selected, Black = unselected)}
  \label{fig:EclipseHeatmap}
\end{figure*}

\section{Conclusion}
The research question we presented was two things.
The RQ1. "Could we estimate profit from Bugzilla without forward looking?". We were able to get a proposal for the demand of custmers in Bugzilla through Priority and Comment. The RQ2. "Could we estimate profit from Bugzilla without forward looking?". We define the Cost in Bugzilla as time. The component's Cost is not accurate. However, the costs are not meaningless given the trends of 2016 and 2017. With this research question, we have built a dataset in the real world for NRP research.

>>>>

\begin{figure*}[h]
\centering
  \begin{subfigure}[b]{0.95\linewidth}
    \includegraphics[width=\linewidth]{images/heatmap_ec.png}
  \end{subfigure}
  \caption{EX3-Requirements Heatmap in ECLIPSE-I(white = selected, Black = unselected)}
  \label{fig:EclipseHeatmap}
\end{figure*}
\begin{figure*}[h]
\centering
  \begin{subfigure}[b]{0.95\linewidth}
    \includegraphics[width=\linewidth]{images/heatmap_ff1.png}
  \end{subfigure}
  \caption{EX3-Requirements Heatmap in FIREFOX-I(white = selected, Black = unselected)}
  \label{fig:EclipseHeatmap}
\end{figure*}
\begin{figure*}[h]
\centering
  \begin{subfigure}[b]{0.95\linewidth}
    \includegraphics[width=\linewidth]{images/heatmap_ff3.png}
  \end{subfigure}
  \caption{EX3-Requirements Heatmap in FIREFOX-III(white = selected, Black = unselected)}
  \label{fig:EclipseHeatmap}
\end{figure*}
\section{Conclusion}
The research question we presented was two things.
The RQ1. "Could we estimate profit from Bugzilla without forward looking?". We were able to get a proposal for the demand of custmers in Bugzilla through Priority and Comment. The RQ2. "Could we estimate profit from Bugzilla without forward looking?". We define the Cost in Bugzilla as time. The component's Cost is not accurate. However, the costs are not meaningless given the trends of 2016 and 2017. With this research question, we have built a dataset in the real world for NRP research.
